---
title: "random_motions"
author: "Dragan Kantar"
date: "12/9/2021"
output: pdf_document
---

```{r}
library(ggplot2)
library(gridExtra)
rm(x_step, y_step, x, y)


# add starting point parameter
# parametrize new step distribution

```



```{r}
n <- 1000    # Number of steps
l <- 1       # Step size distribution parameter

```

## Browninan Walk with Fixed Step Size

```{r}
step_size <- l              # Step size
theta <- runif(n-1)*2*pi    # Angle of direction

x_step <- step_size*cos(theta)    # Distance traveled along x-axis for i-th step
y_step <- step_size*sin(theta)    # Distance traveled along y-axis for i-th step

x <- c(0, cumsum(x_step))    # x-axis position after i-th step
y <- c(0, cumsum(y_step))    # y-axis position after i-th step

```


## Brownian Walk with Negative Exponential Step Size Distribution

```{r}
step_size <- -l*log(runif(n-1)*l)    # Step size
theta <- runif(n-1)*2*pi             # Angle of direction

x_step <- step_size*cos(theta)    # Distance traveled along x-axis for i-th step
y_step <- step_size*sin(theta)    # Distance traveled along y-axis for i-th step

x <- c(0, cumsum(xstep))    # x-axis position after i-th step
y <- c(0, cumsum(ystep))    # y-axis position after i-th step

```

Here, the step size is chosen from a probability distribution. The probability distribution that we will be using here is P(l) = 1/L * e^(-l/L) where l can take any value between 0 and infinity and L is average step size. The integral of P(l) from 0 to infinity is 1 since a probability distribution should be normalized to 1. The average step size is the integral of l*P(l) from 0 to infinity and indeed equals L. This negative exponential probability distribution is light-tailed.

## Levy Flight with Power-Law Step Size Distribution

```{r}
theta <- runif(n-1)*2*pi
alpha <- 3  # try a number between greater than 1 and no more than 3
lmin <- 1
lmax <- 5000
step_size <- runif(n-1, lmax^(-alpha), lmin^(-alpha))^(-1/alpha)

xstep <- step_size*cos(theta)
ystep <- step_size*sin(theta)

x <- c(0, cumsum(xstep))
y <- c(0, cumsum(ystep))

```


Here, the step size is chosen from a probability distribution.The power-law probability distribution that we will be using here is P(l) = A * l^(- alpha) where the step size l lies between lmin and lmax. The factor A assures that the integral of P(l) for l between lmin and lmax equals 1 since a probability distribution should be normalized to 1. Its exact expression/value is not important for the following. Alpha is the exponent of the power law. This power-law distribution is fat-tailed. 

## Descriptive
```{r}
hist(step_size, breaks=200)
mean(step_size)

ggplot(data.frame(x=x, y=y), aes(x, y))+geom_point()+geom_path()

```
